---
output: github_document
editor_options: 
  chunk_output_type: inline
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%",
    eval = TRUE
)
library(magrittr)
```

# drop

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/valid)](https://CRAN.R-project.org/package=valid)
<!-- badges: end -->

## Installation

You can install the development version of from [GitHub](https://github.com/) with:

```{r eval=FALSE}
# install.packages("remotes")
remotes::install_github("rappster/drop")
```

## What?

Drop, i.e. remove, certain values in (nested) list structures.

Experimental and scope is "scratch your own itch".

## Why?

Because I always seem to need it at some point in various other projects and always struggled to find/remember previous implementations that worked. 

## How?

By leveraging [rrapply](https://github.com/JorisChau/rrapply) (see [SO post](https://stackoverflow.com/questions/63231071/recursive-remove-null-elements-of-list-of-lists))

```{r, eval=TRUE}
library(drop)
```

## Drop NULL values

```{r}
x <- list(
    foo = NULL,
    bar = 1,
    baz = TRUE,
    foobar = "a"
)

x %>% drop_null()
```

```{r}
x <- list(
    list(foo = NULL, bar = 1)
)

x %>% drop_null()
```

```{r}
x <- list(
    foo = list(bar = NULL, baz = list(x = 1, y = NULL, z = 3)),
    baz = 2
)

x %>% drop_null()
```

## Drop empty values

```{r}
x <- list(
    foo = integer(),
    bar = 1,
    baz = TRUE,
    foobar = "a"
)

x %>% drop_empty()
```

```{r}
x <- list(
    list(
        foo = character(), bar = 1)
)

x %>% drop_empty()
```

```{r}
x <- list(
    foo = list(bar = logical(), baz = list(x = 1, y = numeric(), z = 3)),
    baz = 2
)

x %>% drop_empty()
```
